---
title: "Uncertain futures"
author: "Rob J Hyndman"
fontsize: 14pt
classoption: aspectratio=169
toc: false
output:
  binb::monash:
    fig_height: 3.5
    fig_width: 7.5
    colortheme: monashwhite
    keep_tex: yes
    includes:
      in_header: aas_header.tex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  cache = TRUE,
  dev.args = list(pointsize = 11)
)
options(digits = 3, width = 88)
library(tidyverse)
library(fpp3)
library(distributional)
library(patchwork)
source("functions.R")
```

```{r cover, include=FALSE}
# Generate plot for title page
pdf(file = "figure/cover.pdf", width = 5, height = 2.5)
austa <- readr::read_csv("http://OTexts.com/fpp3/extrafiles/austa.csv") %>%
  as_tsibble(index = Year)
fit <- austa %>% model(ETS(Visitors))
sim <- fit %>%
  generate(h = 10, times = 20) %>%
  mutate(
    replicate = factor(.rep, levels = 1:20, labels = paste("Future", 1:20))
  )
ggplot(austa, aes(x = Year)) +
  geom_line(aes(y = Visitors, colour = "Data")) +
  geom_line(aes(y = .sim, colour = replicate), data = sim) +
  scale_colour_manual(
    values = c(
      "#000000", "#D55E00", "#0072B2", "#009E73", "#CC79A7", "#E69F00", "#56B4E9", "#F0E442",
      sample(rainbow(13))
    ),
    breaks = c("Data", paste("Future", 1:20)),
    name = " "
  ) +
  guides(color = "none") +
  theme_minimal() +
  scale_y_discrete(breaks = "none") +
  scale_x_discrete(breaks = "none") +
  theme(
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank()
  )
crop::dev.off.crop()
```

```{r get_local, eval=FALSE, include=FALSE}
localcases <- readr::read_csv("~/git/covid19ensemble/inputs/local_cases_input.csv") %>%
  rename(
    n = count,
    date = date_onset
  ) %>%
  # Adjust count to include cases yet to be detected
  mutate(n = n / detection_probability) %>%
  # Remove last days with prob of detection < 0.5
  filter(detection_probability > 0.5) %>%
  as_tsibble(index = date, key = state) %>%
  select(date, state, n) %>%
  filter(state != "AUS")
saveRDS(localcases, "localcases.rds")
```

```{r read_local, echo=FALSE}
localcases <- readRDS("localcases.rds")
```

## What can we forecast?

\only<1>{\fullheight{AusBOM}}
\only<2>{\placefig{0}{1.35}{height=10.8cm, width=20cm}{nasdaq-stock-market}}
\only<3>{\placefig{0}{1.35}{height=11.2cm, width=20cm}{pills}}
\only<4>{\placefig{0}{1.35}{height=9.2cm, width=20cm}{elecwires}
\begin{textblock}{12}(0.2,8.8)\tiny\textcolor{gray}{\texttt{Varistor60, CC BY-SA 4.0, https://commons.wikimedia.org/w/index.php?curid=59368531}}
\end{textblock}}
\only<5>{\placefig{0}{1.35}{height=10.2cm, width=20cm}{12apostles}}
\only<6>{\placefig{0}{1.35}{height=9.2cm, width=20cm}{covid}}

```{r austa}
# Grab ABS data
austa <- readxl::read_excel("340101.xls", sheet="Data1", skip=9) %>%
  rename(date = `Series ID`, value = A85375847A) %>%
  select(date, value) %>%
  transmute(
    Month = yearmonth(date),
    Visitors = value / 1e3
  ) %>%
  bind_rows(tibble(
    Month = yearmonth(seq(as.Date("2021-06-01"), by = "1 month", length = 7)),
    Visitors = NA_real_
  )) %>%
  as_tsibble(index = Month) %>%
  filter(Month >= yearmonth("2000 Jan"))
# Fit ETS model
fit <- austa %>%
  filter(Month < yearmonth("2018 Jan")) %>%
  model(ETS(Visitors))
# Product forecasts
fc <- forecast(fit, h = 48) %>%
  mutate(Month = as.Date(Month))
# Simulate 100 future sample paths
set.seed(1967)
sim <- fit %>%
  generate(h = 48, times = 100) %>%
  mutate(
    replicate = factor(.rep, levels = 1:100, labels = paste("Future", 1:100)),
    .rep = as.numeric(.rep)
  ) %>%
  as_tibble() %>%
  mutate(Month = as.Date(Month))
# Nice colors
cols <- scale_colour_manual(
  values = c("#D55E00", "#0072B2", "#009E73", "#CC79A7", "#E69F00", "#56B4E9", "#F0E442", sample(rainbow(93))),
  breaks = paste("Future", 1:100),
  name = " "
)
# Now build up some plots with alignment
p1 <- austa %>%
  mutate(Visitors = if_else(Month >= yearmonth("2018 Jan"), NA_real_, Visitors)) %>%
  as_tibble() %>%
  mutate(Month = as.Date(Month)) %>%
  ggplot(aes(x = Month, y = Visitors)) +
  geom_line() +
  labs(
    x = "Month",
    y = "Thousands of visitors",
    title = "Total short-term visitors to Australia"
  ) +
  scale_x_date(
    breaks = seq(as.Date("2000-01-01"), by = "5 years", l = 5),
    labels = paste("Jan", seq(2000, 2020, by = 5)),
    minor_breaks = seq(as.Date("2001-01-01"), by = "1 year", l = 25)
  ) +
  ylim(min(austa$Visitors, sim$.sim, na.rm = TRUE), max(austa$Visitors, sim$.sim, na.rm = TRUE))
p2 <- p1 + cols +
  geom_line(aes(y = .sim, group = replicate, colour = replicate),
    data = sim %>% filter(.rep <= 1)
  )
p3 <- p1 + cols +
  geom_line(aes(y = .sim, group = replicate, colour = replicate),
    data = sim %>% filter(.rep <= 2)
  )
p4 <- p1 + cols +
  geom_line(aes(y = .sim, group = replicate, colour = replicate),
    data = sim %>% filter(.rep <= 3)
  )
p5 <- p1 + cols +
  geom_line(aes(y = .sim, group = replicate, colour = replicate),
    data = sim %>% filter(.rep <= 10)
  )
p6 <- p1 + cols +
  geom_line(aes(y = .sim, group = replicate, colour = replicate), alpha = 0.5, data = sim) +
  guides(colour = "none")
p7 <- p1 +
  geom_line(aes(y = .sim, group = replicate, colour = replicate), alpha = 0.5, col = "gray", data = sim) +
  guides(colour = "none")
p8 <- p7 + autolayer(fc, level = c(50, 90))
p9 <- p8 + coord_cartesian(xlim=as.Date(c("2013-01-01","2021-08-01"))) +
  scale_x_date(
    breaks = seq(as.Date("2000-01-01"), by = "2 years", l = 11),
    labels = paste("Jan", seq(2000, 2020, by = 2)),
    minor_breaks = seq(as.Date("2001-01-01"), by = "1 year", l = 25)
  ) 
aligned_plots <- align_patches(p1, p2, p3, p4, p5, p6, p7, p8,p9)
```

## Random futures

\forecast\pause

```{r austa1, dependson="austa"}
aligned_plots[[1]]
```

## Random futures

\forecast

```{r austa2, dependson='austa'}
aligned_plots[[2]]
```

\simfutures

## Random futures

\forecast

```{r austa3, dependson='austa'}
aligned_plots[[3]]
```

\simfutures

## Random futures

\forecast

```{r austa4, dependson='austa'}
aligned_plots[[4]]
```

\simfutures

## Random futures

\forecast

```{r austa5, dependson='austa'}
aligned_plots[[5]]
```

\simfutures

## Random futures

\forecast

```{r austa6, dependson='austa'}
aligned_plots[[6]]
```

\simfutures

## Random futures

\forecast

```{r austa7, dependson='austa'}
aligned_plots[[7]]
```

\simfutures

## Random futures

\forecast

```{r austa8, dependson='austa'}
aligned_plots[[8]]
```

\simfutures

## Random futures

\forecast

```{r austa9, dependson='austa'}
aligned_plots[[9]]
```

\simfutures


## Random futures

\forecast

```{r austa9b, dependson='austa'}
aligned_plots[[9]] +
  geom_line(
    colour = "black",
    data = austa %>% filter(Month >= yearmonth("2018 Jan")) %>% mutate(Month = as.Date(Month))
  )
```

\simfutures



## Forecastability factors
\color{black}

Something is easier to forecast if:

 1. we have a good understanding of the factors that contribute to it, and can measure them.
 2. there is lots of data available;
 3. the future is somewhat similar to the past
 4. the forecasts cannot affect the thing we are trying to forecast.

## Forecasting by maggots

\placefig{0.8}{1.5}{width=8cm}{sheepliverbm}

\only<2>{\begin{textblock}{7}(8.5,1.7)
\raggedright\large\color{black}
\textbf{Clay model of sheep's liver}\\[0.4cm]
Used by Bab\-ylon\-ian forecasters approximately 600 B.C.\\[0.7cm]
Now in \rlap{British Museum.}
\end{textblock}}

## Forecasting by hallucination

\only<1->{\placefig{0}{1.35}{height=8.25cm, width=20cm}{delphitemple}}
\only<2>{\placefig{7}{1.35}{height=7.77cm, width=20cm}{1106}}

## Forecasting and the law

\placefig{10.1}{1.35}{width=6cm, height=20cm}{250px-Constance_II_Colosseo_Rome_Italy}

\begin{textblock}{8}(1,1.8)\raggedright
\begin{block}{}
\color{black}
Anyone who consults a soothsayer on account of curiosity of the future will suffer capital punishment.

\mbox{}\hfill\emph{Codex Theodosianus 9.16.4}
\end{block}
\end{textblock}

## International Journal of Forecasting

\only<1>{\placefig{0}{1.35}{height=8.cm, width=20cm}{IJFcover}}

\begin{textblock}{8}(7,2)\fontsize{16}{17}\sf
\begin{block}{}
\begin{itemize}
\item Editor-in-Chief: 2005--2018
\item Impact factor 2004: 0.4
\item Impact factor 2018: 3.4
\end{itemize}
\end{block}
\end{textblock}


## More information
\fontsize{20}{24}\sf

\href{https://robjhyndman.com}{\faicon{home} robjhyndman.com}

\href{https://twitter.com/robjhyndman}{\faicon{twitter} @robjhyndman}

\href{https://github.com/robjhyndman}{\faicon{github}  @robjhyndman}

\href{mailto:rob.hyndman@monash.edu}{\faicon{envelope}  rob.hyndman@monash.edu}

\vspace*{0.8cm}\fontsize{19}{19}\sf

###
Slides: \texttt{\href{https://robjhyndman.com/aas2021}{robjhyndman.com/aas2021}}

