---
title: "Uncertain futures: what can we forecast and when should we give up?"
author: "Rob J Hyndman"
fontsize: 14pt
classoption: aspectratio=169
toc: true
output:
  binb::monash:
    fig_height: 3.5
    fig_width: 7.5
    colortheme: monashwhite
    keep_tex: yes
    includes:
      in_header: header.tex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  cache = TRUE,
  dev.args = list(pointsize = 11)
)
options(digits = 3, width = 88)
library(tidyverse)
library(fpp3)
library(distributional)
library(gganimate)
library(patchwork)
source("functions.R")
```

```{r get_local, eval=FALSE, include=FALSE}
localcases <- readr::read_csv("~/git/covid19ensemble/inputs/local_cases_input.csv") %>%
    rename(
      n = count,
      date = date_onset
    ) %>%
    # Adjust count to include cases yet to be detected
    mutate(n = n / detection_probability) %>%
    # Remove last days with prob of detection < 0.5
    filter(detection_probability > 0.5) %>%
    as_tsibble(index = date, key = state) %>%
  select(date, state, n) %>%
  filter(state != "AUS")
saveRDS(localcases,"localcases.rds")
```

```{r read_local, echo=FALSE}
localcases <- readRDS("localcases.rds")
```

# What can we forecast?

## What can we forecast?

\fullheight{AusBOM}

## What can we forecast?

\placefig{0}{1.35}{height=10.8cm, width=20cm}{nasdaq-stock-market}

## What can we forecast?

\placefig{0}{1.35}{height=10.2cm, width=20cm}{Forex2}

## What can we forecast?

\placefig{0}{1.35}{height=11.2cm, width=20cm}{pills}

## What can we forecast?

\placefig{0}{1.35}{height=9.2cm, width=20cm}{elecwires}
\begin{textblock}{12}(0.2,8.8)\tiny\textcolor{gray}{\texttt{Varistor60, CC BY-SA 4.0, https://commons.wikimedia.org/w/index.php?curid=59368531}}
\end{textblock}

## What can we forecast?

\placefig{0}{1.35}{height=10.7cm, width=20cm}{bocsar}

## What can we forecast?

\placefig{0}{1.35}{height=10.7cm, width=20cm}{monash_students}

## What can we forecast?

\placefig{0}{1.35}{height=10.2cm, width=20cm}{12apostles}

## What can we forecast?

\placefig{0}{1.35}{height=9.2cm, width=20cm}{covid}

# Forecastability factors

## Which is easiest to forecast?

 * daily electricity demand in 3 days time
 * timing of next Halley's comet appearance
 * time of sunrise this day next year
 * Google stock price tomorrow
 * Google stock price in 6 months time
 * maximum temperature tomorrow
 * exchange rate of \$US/AUS next week
 * total sales of drugs in Australian pharmacies next month

\vspace*{10cm}

## Which is easiest to forecast?

 1. time of sunrise this day next year
 2. timing of next Halley's comet appearance
 3. maximum temperature tomorrow
 4. daily electricity demand in 3 days time
 5. total sales of drugs in Australian pharmacies next month
 6. Google stock price tomorrow
 7. exchange rate of \$US/AUS next week
 8. Google stock price in 6 months time

\only<2>{\begin{block}{}\begin{itemize}\tightlist
 \item how do we measure ``easiest''?
 \item what makes something easy/difficult to forecast?
 \end{itemize}\end{block}}

\vspace*{10cm}

## Forecastability factors
\color{black}

Something is easier to forecast if:

 1. we have a good understanding of the factors that contribute to it
 2. there is lots of data available;
 3. the future is somewhat similar to the past
 4. the forecasts cannot affect the thing we are trying to forecast.

# Forecasting is difficult

## Reputations can be made and lost

\begin{block}{}``I think there is a world market for maybe
    five computers.'' \newline{\null\hfill\small (Chairman of IBM,
    1943)}\end{block}\pause

\begin{block}{}``There is no reason anyone would want a
    computer in their home.'' \newline\null\hfill{\small (President, DEC,
    1977)}\end{block}\pause

\begin{alertblock}{}``We're going to be opening relatively soon \dots The virus \dots\ will go away in April.''\hfill{\small (Donald Trump, February 2020)}\end{alertblock}\pause

\begin{alertblock}{}``We expect that Australians will be fully vaccinated by the end of October.''\hfill{\small (Scott Morrison, December 2020)}\end{alertblock}

## Forecasting is difficult

\fullheight{hopecasts}

## Improving forecasts

\fullheight{ncep-skill}

# The statistical forecasting perspective

```{r austa}
# Grab ABS data
austa <- readabs::read_abs(series_id = "A85375847A") %>%
  select(date, value) %>%
  transmute(
    Month = yearmonth(date),
    Visitors = value/1e3
  ) %>%
  bind_rows(tibble(
    Month = yearmonth(seq(as.Date("2021-06-01"), by="1 month", length=7)),
    Visitors = NA_real_
  )) %>%
  as_tsibble(index=Month) %>%
  filter(Month >= yearmonth("2000 Jan"))
# Fit ETS model
fit <- austa %>%
  filter(Month < yearmonth("2018 Jan")) %>%
  model(ETS(Visitors))
# Product forecasts
fc <- forecast(fit, h=48) %>%
  mutate(Month = as.Date(Month))
# Simulate 100 future sample paths
sim <- fit %>% generate(h = 48, times = 100) %>%
  mutate(
    replicate = factor(.rep, levels = 1:100, labels = paste("Future", 1:100)),
    .rep = as.numeric(.rep)
  ) %>%
  as_tibble() %>%
  mutate(Month = as.Date(Month))
# Nice colors
cols <- scale_colour_manual(values = c("#D55E00", "#0072B2","#009E73", "#CC79A7", "#E69F00", "#56B4E9", "#F0E442",sample(rainbow(93))),
                      breaks = paste("Future", 1:100),
                      name = " ")
# Now build up some plots with alignment
p1 <- austa %>%
  mutate(Visitors = if_else(Month >= yearmonth("2018 Jan"), NA_real_, Visitors)) %>%
  as_tibble() %>%
  mutate(Month = as.Date(Month)) %>%
  ggplot(aes(x=Month, y=Visitors)) +
  geom_line() +
  labs(
    x = "Month",
    y = "Thousands of visitors",
    title = "Total short-term visitors to Australia"
  ) +
  scale_x_date(
    breaks = seq(as.Date("2001-01-01"), by="5 years", l=5),
    labels = paste("Jan",seq(2000,2020,by=5)),
    minor_breaks = seq(as.Date("2001-01-01"), by="1 year", l=25)) +
  ylim(min(austa$Visitors, sim$.sim, na.rm = TRUE), max(austa$Visitors, sim$.sim, na.rm = TRUE)) 
p2 <- p1 + cols +
  geom_line(aes(y = .sim, group=replicate, colour = replicate),
            data = sim %>% filter(.rep<=1))
p3 <- p1 + cols +
  geom_line(aes(y = .sim, group=replicate, colour = replicate),
            data = sim %>% filter(.rep<=2))
p4 <- p1 + cols +
  geom_line(aes(y = .sim, group=replicate, colour = replicate),
            data = sim %>% filter(.rep<=3))
p5 <- p1 + cols +
  geom_line(aes(y = .sim, group=replicate, colour = replicate),
            data = sim %>% filter(.rep<=10))
p6 <- p1 + cols +
  geom_line(aes(y = .sim, group=replicate, colour = replicate), alpha=0.5, data = sim) +
  guides(colour="none")
p7 <- p1 + 
  geom_line(aes(y = .sim, group=replicate, colour = replicate), alpha=0.5, col='gray', data = sim) +
  guides(colour="none")
p8 <- p7 + autolayer(fc)
aligned_plots <- align_patches(p1,p2,p3,p4,p5,p6,p7,p8)
```

## Random futures

\forecast\pause

```{r austa1, dependson="austa"}
aligned_plots[[1]]
```

## Random futures

\forecast

```{r austa2, dependson='austa'}
aligned_plots[[2]]
```

\simfutures

## Random futures

\forecast

```{r austa3, dependson='austa'}
aligned_plots[[3]]
```

\simfutures

## Random futures

\forecast

```{r austa4, dependson='austa'}
aligned_plots[[4]]
```

\simfutures

## Random futures

\forecast

```{r austa5, dependson='austa'}
aligned_plots[[5]]
```

\simfutures

## Random futures

\forecast

```{r austa6, dependson='austa'}
aligned_plots[[6]]
```

\simfutures

## Random futures

\forecast

```{r austa7, dependson='austa'}
aligned_plots[[7]] 
```

\simfutures

## Random futures

\forecast

```{r aust8, dependson='austa'}
aligned_plots[[8]] 
```

\simfutures

## Random futures

\forecast

```{r austa9, dependson='austa'}
aligned_plots[[8]] + geom_line(colour="black", 
  data=austa %>% filter(Month >= yearmonth("2018 Jan")) %>% mutate(Month = as.Date(Month))
)
```

\simfutures

# PBS forecasting

## PBS forecasting

### The Pharmaceutical Benefits Scheme (PBS) is the Australian government drugs subsidy scheme.

  * Many drugs bought from pharmacies are subsidised to allow more equitable access to modern drugs.
  * The cost to government is determined by the number and types of drugs purchased. Currently nearly 1\% of GDP.
  * The total cost is budgeted based on forecasts of drug usage.

## PBS forecasting
\fullheight{pbs2}

## PBS forecasting

  * In 2001: \$4.5 billion budget, under-forecasted by \$800 million.
  * Thousands of products. Seasonal demand.
  * Subject to covert marketing, volatile products, uncontrollable expenditure.
  * Although monthly data available for 10 years, data are aggregated to annual values, and only the first three years are used in estimating the forecasts.
  * All forecasts being done with the \texttt{FORECAST} function in MS-Excel!

## ATC drug classification

\hspace*{-1cm}\begin{minipage}{9.6cm}
\begin{tikzpicture}
\tikzstyle{every node}=[ellipse,font=\small,draw,fill=red!15]
\tikzstyle[level font=\small,set style={{every node}+=[fill=blue!15]}]
\tikzstyle{level 1}=[font=\small,set style={{every node}+=[fill=blue!15]}]
\tikzstyle{level 2}=[font=\small,set style={{every node}+=[fill=yellow]}]
\node[label=right:\hspace*{-0.cm}Alimentary tract and metabolism,label=left:\textbf{14 classes}\hspace*{0.3cm}]{A}[edge from parent fork down]
   child {node[label=right:\hspace*{-0.0cm}Drugs used in diabetes,label=left:\textbf{84 classes}]{A10}
     child {node[label=right:\hspace*{-0.35cm}Blood glucose lowering drugs]{A10B}
       child {node[label=right:\hspace*{0.1cm}Biguanides]{A10BA}
         child {node[label=right:\hspace*{-0.15cm}Metformin]{A10BA02}
 }}}};
 \end{tikzpicture}
\end{minipage}

## ETS forecasts of PBS data

```{r pbs1}
pbs <- PBS %>%
  group_by(ATC2) %>%
  summarise(Cost = sum(Cost)) %>%
  ungroup()
pbs %>%
  filter(ATC2 == "A10") %>%
  model(ETS(Cost)) %>%
  forecast(h="3 years") %>%
  autoplot(pbs)
```

## ETS forecasts of PBS data

```{r pbs2}
pbs %>%
  filter(ATC2 == "A05") %>%
  model(ETS(Cost)) %>%
  forecast(h="3 years") %>%
  autoplot(pbs)
```

## ETS forecasts of PBS data

```{r pbs3}
pbs %>%
  filter(ATC2 == "D01") %>%
  model(ETS(Cost)) %>%
  forecast(h="3 years") %>%
  autoplot(pbs)
```

## ETS forecasts of PBS data

```{r pbs4}
pbs %>%
  filter(ATC2 == "S01") %>%
  model(ETS(Cost ~ trend("N"))) %>%
  forecast(h="3 years") %>%
  autoplot(pbs)
```

## ETS forecasts of PBS data

```{r pbs5}
pbs %>%
  filter(ATC2 == "R03") %>%
  model(ETS(Cost)) %>%
  forecast(h="3 years") %>%
  autoplot(pbs)
```

## ETS forecasts of PBS data

```{r pbs6}
pbs %>%
  filter(ATC2 == "H02") %>%
  model(ETS(Cost)) %>%
  forecast(h="3 years") %>%
  autoplot(pbs)
```

## Forecasting the PBS
\fontsize{14}{15}\sf

  * Developed an automatic forecasting algorithm for exponential smoothing state space models based on the AIC.
  * Exponential smoothing models allowed for time-changing trend and seasonal patterns.
  * Forecast MAPE reduced from 15--20% to 0.6%.
  * State space models provide prediction intervals which give a sense of uncertainty.
  * Theory and algorithm published as Hyndman et al (IJF, 2002).
  * Now implemented in R as `ets()` in forecast package, as `ETS()` function in fable package, and in Tableau and elsewhere.
  * NOT implemented in `FORECAST.ETS` function in MS-Excel.

## Hierarchical forecasting

\hspace*{-1cm}\begin{minipage}{9.6cm}
\begin{tikzpicture}
\tikzstyle{every node}=[ellipse,font=\small,draw,fill=red!15]
\tikzstyle[level font=\small,set style={{every node}+=[fill=blue!15]}]
\tikzstyle{level 1}=[font=\small,set style={{every node}+=[fill=blue!15]}]
\tikzstyle{level 2}=[font=\small,set style={{every node}+=[fill=yellow]}]
\node[label=right:\hspace*{-0.cm}Alimentary tract and metabolism,label=left:\textbf{14 classes}\hspace*{0.3cm}]{A}[edge from parent fork down]
   child {node[label=right:\hspace*{-0.0cm}Drugs used in diabetes,label=left:\textbf{84 classes}]{A10}
     child {node[label=right:\hspace*{-0.35cm}Blood glucose lowering drugs]{A10B}
       child {node[label=right:\hspace*{0.1cm}Biguanides]{A10BA}
         child {node[label=right:\hspace*{-0.15cm}Metformin]{A10BA02}
 }}}};
 \end{tikzpicture}
\end{minipage}

## Hierarchical forecasting

  * Nearly ten years later, Hyndman et al (CSDA, 2011) proposed forecast reconciliation to handle hierarchical time series.
  * Now widely used in business and industry and implemented in the `hts` and `fable` packages.

# COVID19 case forecasting

## Data sources

* Case-level data of all positive COVID-19 tests: onset and detection times.
* Daily population mobility data from Google, Apple & Facebook
* Weekly non-household contact surveys
* Weekly behavioural surveys
* Daily case numbers from many countries and regions via the Johns Hopkins COVID-19 repository

## Case numbers
\fontsize{12}{12}\sf

```{r, echo=TRUE}
localcases %>% filter(state == "VIC", date >= "2020-07-01")
```

## Case numbers

```{r, echo=FALSE, fig.height=2.9}
state_colours <- c(
  NSW = "#56b4e9",
  VIC = "#0072b2",
  QLD = "#009e73",
  SA = "#f0e442",
  NT = "#d55e00",
  WA = "#e69f00",
  TAS = "#cc79a7",
  ACT = "#cccccc"
)
localcases %>%
  autoplot(n) +
  labs(x="Date of symptom onset") +
  scale_color_manual(values = state_colours)
```

* Recent case numbers are uncertain and incomplete as date of onset is not known until symptoms show and a test is obtained.


## Global daily cases by region from Johns Hopkins

\begin{alertblock}{}https://github.com/CSSEGISandData/COVID-19
\end{alertblock}

\full{jhu_dashboard}

## Model 3: Global AR model (Monash)
\fontsize{14}{16}\sf

* Uses Johns Hopkins data from countries and regions with sufficient data.
* Series with obvious anomalies (negative cases and large step changes) removed.
* $n_{t,i}=$ daily cases on day $t$ in country/region $i$ (scaled so all data have same mean and variance).
* $y_{t,i} = \phi_1 y_{t-1,i} + \cdots +\phi_p y_{t-p,i} + \varepsilon_{t,i}$\newline where $y_{t,i} = \log(n_{t,i}+0.5)$ and $\varepsilon_{t,i}\sim N(0,\sigma_i^2)$.
* No stationarity constraints. Common coefficients.
* Current model has $p=24$ (selected to minimize the 7-day-ahead MAE on recent Australian data).

## Forecasting ensemble
\fontsize{14}{17}\sf

* Forecasts obtained from a mixture distribution of the component models.
$$\tilde{p}(y_{t+h}|I_t) = \sum_{k=1}^3 w_{t+h|t,k} p_k(y_{t+h}|I_t)$$
where $p_k(y_{t+h}|I_t)$ is the forecast distribution from model $k$, $I_t$ denotes the data available at time $t$ and the weights $w_{t+h|t,k}>0$ sum to one.
* Also known as "linear pooling"
* Works best when individual models are over-confident and use different data sources.
* We have used equal weights $w_{t+h|t,k}=1/3$.


## Ensemble forecasts: Victoria

```{r combined_forecasts, eval=FALSE}
# Read weekly samples files from mediaflux and save as rds file
fs::dir_ls("~/mediaflux", glob = "*.csv") %>%
  stringr::str_subset("combined_samples_202") %>%
  purrr::map_dfr(read_csv) %>%
  nest(sample = sim1:sim2000) %>%
  group_by(date, state, .model, forecast_origin) %>%
  mutate(sample = list(unname(unlist(sample)))) %>%
  ungroup() %>%
  saveRDS(file = "samples.rds")
```

```{r read_samples}
samples <- readRDS("samples.rds")
ensemble <- make_ensemble(samples)
```

```{r some_plots, include=FALSE}
vic_ensemble <- ensemble %>% filter(state == "VIC")
origins <- sort(unique(vic_ensemble$forecast_origin))
for (i in seq_along(origins)) {
  p <- vic_ensemble %>%
    filter(forecast_origin == origins[i], date <= origins[i] + 7 * 4) %>%
    mutate(dist = dist_sample(sample)) %>%
    select(-sample) %>%
    as_fable(
      index = date, key = forecast_origin,
      response = "n", distribution = dist
    ) %>%
    autoplot(level = c(50, 60, 70, 80, 90), point_forecast = lst(median)) +
    autolayer(
      filter(localcases, state == "VIC",
             date >= origins[i] - 7 * 12, date <= origins[i] + 7 * 4),
      n
    ) +
    scale_x_date(
      breaks = seq(as.Date("2020-01-01"), by = "1 month", l = 24),
      minor_breaks = NULL,
      labels = paste(
        rep(c("Jan","Feb","Mar","Apr","May","Jun","Jul","Aug","Sep","Oct","Nov","Dec"), 2),
        rep(2020:2021, c(12,12))
      )
    ) +
    theme(legend.position = "none") +
    xlab("Date of symptom onset") + ylab("Number of cases")
  pdf(paste0(here::here("figure"), "/ensemble", i, ".pdf"),
    width = 20 / 2.54, height = 10 / 2.54
  )
  print(p)
  crop::dev.off.crop()
}
```

\only<1>{\full{ensemble2}}
\only<2>{\full{ensemble8}}
\only<3>{\full{ensemble11}}
\only<4>{\full{ensemble33}}
\only<5>{\full{ensemble48}}
\only<6>{\full{ensemble88}}
\only<7>{\full{ensemble106}}

<!-- \centerline{\animategraphics[controls,buttonsize=0.3cm,width=14cm]{5}{figs/ensemble}{1}{107}} -->

## Evaluating probabilistic forecasts

\begin{textblock}{9.5}(0.2,1.2)
\begin{alertblock}{}\vspace*{-0.2cm}
\begin{align*}
f_{p,t} &= \text{quantile forecast with prob. $p$ at time $t$.}\\
y_{t} &= \text{observation at time $t$}
\end{align*}
\end{alertblock}\vspace*{-0.3cm}
\uncover<2->{\begin{block}{Quantile score}\vspace*{-0.1cm}
$$
  Q_{p,t} = \begin{cases}
  2(1 - p) \big|y_t - f_{p,t}\big|, & \text{if $y_{t} < f_{p,t}$}\\
  2p \big|y_{t} - f_{p,t}\big|, & \text{if $y_{t} \ge f_{p,t}$} \end{cases}
$$
\end{block}}
\end{textblock}
\begin{textblock}{15}(0.2,5.8)
\uncover<4->{
\begin{itemize}\itemsep=0cm\parskip=0cm
\item Low $Q_{p,t}$ is good
\item Multiplier of 2 often omitted, but useful for interpretation
\item $Q_{p,t}$ like absolute error (weighted to account for likely exceedance)
\item Average $Q_{p,t}$ over $p$ = CRPS (Continuous Ranked Probability Score)
\end{itemize}}
\end{textblock}
\begin{textblock}{6}(10,2)
\only<3->{\animategraphics[loop,autoplay]{10}{uncertain_futures_files/figure-beamer/pinball-}{1}{100}}
\end{textblock}

```{r pinball, eval=FALSE, echo=FALSE, fig.show='animate', interval=1/10, message=FALSE, fig.height=3, fig.width=5, cache=FALSE}
# Turn eval=TRUE to recompute these graphs. They are loaded in the above animategraphics call.
prob <- seq(0.05, 0.95, by = 0.05)
df <- expand.grid(
    error = c(-10, 0, 10),
    p = c(prob, rev(head(prob, -1)[-1]))
  ) %>%
  mutate(
    state = rep(seq(length(p) / 3), rep(3, length(p) / 3)),
    qpt = 2 * p * error * (error > 0) - 2 * (1 - p) * error * (error < 0)
  )
labels <- df %>%
  select(p, state) %>%
  distinct() %>%
  mutate(label = paste0("p = ", sprintf("%.2f", p)))
df %>% ggplot(aes(x = error, y = qpt)) +
  geom_line(aes(group = state), colour = "red") +
  labs(
    x = latex2exp::TeX("Error: $y_t - f_{p,t}$"),
    y = latex2exp::TeX("Q_{p,t}")
  ) +
  geom_label(data = labels, aes(x = 0, y = 17, label = label)) +
  transition_states(state)
```

## CRPS: Continuous Ranked Probability Score
\vspace*{-0.8cm}\fontsize{13}{14}\sf\color{black}
\begin{align*}
y_{t} &= \text{observation at time $t$}\\
F_{t}(u) &= \text{Pr}(Y_{t} \le u) = \text{forecast distribution}\\
f_{p,t} &= F^{-1}_t(p) = \text{quantile forecast with prob. $p$}\\
  Q_{p,t} &= \begin{cases}
  2(1 - p) \big|y_t - f_{p,t}\big|, & \text{if $y_{t} < f_{p,t}$}\\
  2p \big|y_{t} - f_{p,t}\big|, & \text{if $y_{t} \ge f_{p,t}$} \end{cases} \\
Y_t \text{ and } Y_t^* &\sim \text{iid with distribution $F_t$.}
\end{align*}

###
\begin{align*}
 \text{CRPS}_t
   & = \int_0^1 Q_{p,t}\, dp \\
   & = \int_{-\infty}^\infty \left[F_t(u) - 1_{y_t \le u}\right]^2 du \\
   & = \textstyle\text{E}|Y_t-y_t| - \frac{1}{2}\text{E}|Y_t-Y_t^*|
\end{align*}

## CRPS: Continuous Ranked Probability Score

```{r crps}
crps <- bind_rows(
  ensemble %>% sample_crps(localcases) %>% mutate(Model = "Ensemble"),
  samples %>% filter(.model == "gar") %>% sample_crps(localcases) %>% mutate(Model = "Global AR"),
  samples %>% filter(.model == "moss") %>% sample_crps(localcases) %>% mutate(Model = "SEEIIR"),
  samples %>% filter(.model == "uoa") %>% sample_crps(localcases) %>% mutate(Model = "Generative")
)
```

```{r crps_plot, fig.height=4.6, fig.width=10}
crps %>%
  filter(
    h >= 1, h <= 20,
    state %in% c("NSW", "QLD", "SA", "VIC")
  ) %>%
  ggplot(aes(x = h, y = crps, group = Model, col = Model)) +
  geom_line() +
  facet_wrap(. ~ state, scales="free_y") +
  labs(x = "Forecast horizon (days)", y = "CRPS") +
  scale_color_manual(values = c("#D55E00", "#0072B2","#009E73", "#CC79A7"))
```

\begin{textblock}{14.5}(0.5,8)
\begin{block}{}
For weekly forecasts created from 17 September 2020 to 15 June 2021
\end{block}
\end{textblock}

## What have we learned?

* Diverse models in an ensemble are better than one model, especially when they use different information.
* Understand the data, learn from the data custodians.
* Have a well-organized workflow for data processing, modelling and generation of forecasts, including version control and reproducible scripts.
* Communicating probabilistic forecasts is difficult, but consistent visual design is helpful.

## When should we give up?
\large

* When there is insufficient data?
* When the models give implausible forecasts?
* When the forecast uncertainty is too large to assist decision making?

## More information
\fontsize{20}{24}\sf

\href{https://robjhyndman.com}{\faicon{home} robjhyndman.com}

\href{https://twitter.com/robjhyndman}{\faicon{twitter} @robjhyndman}

\href{https://github.com/robjhyndman}{\faicon{github}  @robjhyndman}

\href{mailto:rob.hyndman@monash.edu}{\faicon{envelope}  rob.hyndman@monash.edu}
